### 2017-03-02 Lab_2/solutions/L2-7-1.tex
Modified some L2 answers, cleaned up the L2 traces. Apart from 2-5-2 L2 is roughly finished
Former-commit-id: 147b063b2b4b0cc6af7827f13c3c03686ff0b711

We observed packets of both ping sessions, from the first session only the replies were caught on the monitor interface and for the second session, all ping packets were seen by the monitor.\\
%
Not seeing the ping requests of the first ping session could be due to failed demodulations at the monitor, causing it to be not be able to detect the modulated
messages sent by STA1 in the first ping session. Because the second ping transmission does originate at STA2, it is less of an issue and that ping traffic is captured without issue.
%
The sniffer machine is not in range of the target wireless devices, or there's too much interference, so the sniffer machine's radio
can't successfully demodulate the transmissions. Note that the increasing use of beamforming helps devices steer their RF energy right
to where the intended receiver is, which means less of that energy goes to where the sniffer machine is, meaning the sniffer will
get a worse signal:noise ratio, and less likelihood of demodulating packets sent at the highest data rates.

>>>>

We observed packets of both ping sessions, from the first session only the replies were caught on the monitor interface and for the second session, all ping packets were seen by the monitor.\\
%
Not seeing the ping requests of the first ping session could be due to failed demodulations at the monitor. Across multiple attemps almost all of STA2's ICMP packets were missed while the other STAs' were almost all captured. This could be related to STA1 and STA3 being close to each other and STA2 being farther away.
%
Failure to capture/demodulate STA2's packets may be related to the use of beamforming in 802.11n. This helps devices steer their RF energy right
to where the intended receiver is, and not to the monitor. This means the monitor will
get a worse signal to noise ratio, making is harder to demodulate packets sent at the highest data rates. We are however not sure whether the devices use/support beamforming.
